Nanophotonic Computational Design

### 2013-03-03 paper/paper.tex
Starting on results.

\section{Results}

\section{Conclusion}

>>>>

\section{Results}
We demonstrate the effectiveness of our design method 
    by produce designs for a variety of nanophotonic devices.

All of our results are in three dimensions
    and consist of a 250 nm etched silicon slab
    completely surrounded by silica.
The permittivity values of silicon and silica used
    were $\epsilon_\text{Si} = 12.25$ and $\epsilon_\text{SiO$_2$} = 2.25$
    respectively.

Many, if not all, of the produced designs exhibit 
    novel functionality, high efficiency ($>80\%$), and 
    very compact footprints of only a few square vacuum wavelengths;
    while still remaining manufacturable.
We also show that many devices can be designed
    to exhibit different functionality for different input excitations.
Additionally, we show that devices can be designed with large tolerances for
    errors in wavelength, temperature and fabrication.

% Runtimes for the design process ranged from 8-80 hours 
%     based on the size of the design space.

\subsection{TE mode converter}
Our first result was a mode conversion device operating in the TE polarization,
    which we define as that mode where the primary E-field component
    of the waveguide mode is polarized in the plane of the structure.

Our performance specification (\fig{3Db_wgc_te}) 
    for the device was for 90\% to 100\% of the 
    input power to be transferred from the fundamental waveguide mode,
    to the second-order waveguide mode.
At the same time, we specified that no more than 1\% of the input power
    was to remain in the transmitted fundamental mode.

\myfig{3Db_wgc_te}
    {Perfomance specification of the TE mode converter.
    Input mode is the fundamental TE-polarized mode on the left.
    Primary output mode is the second-order mode on the right.
    Output power in the transmitted fundamental mode on the right 
    above 1\% is to be rejected.
    The structure shown is the final three-dimensional design.
    }

\myfig{takeaway}
    {Structure and E-field at the central plane of the device.
    The conversion efficiency into the second-order mode is 86.4\%,
    while the power into the rejection mode (fundamental) is 0.7\%.}

\section{Conclusion}
Conclusion
